---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Joshua Nahm"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_orig, aes(x = Date, y = Cases_Total)) + geom_point()
```

If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_orig |> 
  filter(State == "CA") |> 
  ggplot(aes(x = Date, y = Cases_Total, color = Cases_Asian)) + geom_line()
```

1. Write code for a plot and describe what you observe?
covid_data_orig |> 
filter(State == "CA") |> 
ggplot(aes(x = Date, y = Cases_Total, color = Cases_Asian)) + geom_line()

Based on the graph above, we can see that as time passes, the total number of Covid-19 cases among the Asian population in California is increasing.

2. Are there any conclusions you can draw?
Based on the description of the first graph provided, one can conclude that the total number of Covid-19 cases is increasing as time passes.

3. What were you not able to do due to not having the R knowledge?
Without the R knowledge, I wasn't able to generate or display graphical outputs such as plots, charts, or graphs. Moreover, I wasn't able to make specific graphs when I needed to look for specific data. 

4. What other data would be useful to better understand this data?
One data what would be useful to better understand this data is Age. Adding a variable such as age will provide more detailed data.


